CDIPS. I. Light Curves in Open Clusters from TESS Sectors 6 \& 7

### 2019-08-03 paper_I/ms.tex
minor

Table~\ref{tbl:s6_lcs} shows the clusters in Sector 6 with the largest
numbers of light curves. The top four clusters are all moving groups
or stellar associations from \citet{dias_proper_2014}: Platais~5,
Platais~6, Mamajek~3, and Collinder~70.  These membership claims
should be regarded with serious skepticism on a source-by-source
basis.  For Platais~6, \citet{Kharchenko_et_al_2013} claimed only
about 400 probable members (1$\sigma$) to exist within the angular
radius of the cluster.  Mamajek~3 (= 32$\,$Ori) similarly has only
about 50 confirmed members \citep{bell_32ori_2017}.

>>>>

Table~\ref{tbl:s6_lcs} shows the clusters in Sector 6 with the largest
numbers of light curves. The top four clusters are all moving groups
or stellar associations from \citet{dias_proper_2014}: Platais~5,
Platais~6, Mamajek~3, and Collinder~70.  These membership claims
should be regarded with serious skepticism.  For Platais~6,
\citet{Kharchenko_et_al_2013} claimed only about 400 probable members
(1$\sigma$) to exist within the angular radius of the cluster.
Mamajek~3 (= 32$\,$Ori) similarly has only about 50 confirmed members
\citep{bell_32ori_2017}.
Some rich open clusters in the Sector 6 field with many light curves,
and more reliable membership lists include Trumpler~5,
Collinder~69 (the $\lambda$ Orionis cluster), and NGC~2287.
